%        File: PS.tex
%     Created: Thu Aug 18 03:00 PM 2011 C
% Last Change: Thu Aug 18 03:00 PM 2011 C
%
\documentclass[a4paper]{article}

\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[USenglish]{babel}

\usepackage[colorlinks]{hyperref}
\usepackage[left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm]{geometry}

\author{Yetian Huang}
\title{Personal Statement}
\date{August 22, 2011}
\begin{document}
\maketitle
Science and technology leads our life. Excited about varieties of
high-tech products, I felt since my childhood destined to become a
scientist or engineer. The advanced technology and excellent teaching
method of universities in the United States always spurred me to strive for
a more convenient life in future. I write this statement in hope of pursuing a
Master Degree on YYY University's Computer Science (CS) program. 

It is not an easy task to locate one's exact interest. While attending
Harbin Institute of Technology, which is known for its aerospace and
military technology, I was admitted to specialize in an advanced field
named Electronic Science and technology. After four semesters'
courses, however, I realized my major was actually an alias of Optical
Engineering, of which most of specialized courses were about optics. I
consulted my conscience in the junior year: Is it exactly what I would
like to devote myself to? Not really. To resolve the issue, I 
browsed series of books in diverse fields. Luckily enough, it was the
experience in the Microsoft Technology Club that brought me to the
magical world of CS. By communicating with the programmers and following the
enthusiastic instruction about their product---an instant
message software for school secondhand sales, I was 
determined to study CS. 

During the last year at university, I spent most of the spare time
updating knowledge of CS on my own. Fortunately, the skill to study by
myself helped me a lot overcome the difficulties with up to ten most
important courses. For example, Data Structure is a preliminary but
panic course in CS, which costs me much time on understand the
procedure of algorithms. So in addition to read the textbook, I also
programmed and verified these algorithms on computers; the efforts
significantly boosted the comprehension of the theories. Consequently,
in the national entrance exam of postgraduate, I defeated many CS
major students and was admitted for graduate education.

An amount of programming skill and problem analysis ability is
indispensable to qualified CS major students. In the last semester
before graduation from university, I was fascinated in the programming
all sorts of algorithms and projects on while other roommates enjoyed
the final depraved time on computer games and movies. Afterwards in my
first year of postgraduate, I led and collaborated with 3 other
classmates over several small scale course projects. Unlike developing
alone, the small projects involved in discussion of the problem, the
division of labor, the coordination in development. The teamwork
process benefited me a lot and must help me solve other problems
encountered in future. 

In my current Master's thesis, I intensively delve into
\textit{feature extraction method for human wrist pulse}. The subject
aims to analyze the characteristics of wrist waveforms of people with
unequal health conditions. I have been through hundreds of papers and
tested my ideas repeatedly. Work is still going on. The nearly one
year's endeavor taught me how to do academic research. I clearly 
realized that current academic atmosphere in China has a long way to
ameliorate. To some extent, I need a better research environment, and that
is what your program could provide.


My intention for applying to graduate education in YYY school is to
both inspire my creativity for future work and extend my interest on
further research. As I profoundly look into the CS program in your
school, The flexible curriculum plan and nurturing academic aura
arrest my desire to receive an exceptional education there. I hope,
after training in your program, I have interest to further research on
specific domain or otherwise return to my motherland to contribute
what I have learned. 

\end{document}


